Well-quasi-orderings on word languages

### 2025-10-16 src/infixes.tex
fix: incorrect proof infixes thue morse width

    Now, let us prove that these bounds are tight. It is clear that
    $\oHeight{\LMorse} = \omegaOrd$: given any number $n \in \Nat$, one can construct a
    \kl{decreasing sequence} of words in $\LMorse$ of length $n$, for instance by
    considering the first $n$ prefixes of the \kl{Thue-Morse sequence} by
    decreasing size.
    Let us now prove that $\oWidth{\LMorse} = \omegaOrd$. Assume by contradiction that
    $\oWidth{\LMorse}$ is finite. Then, $\LMorse$ can be written as a finite union of
    \kl{chains} for the \kl{infix relation}, and in particular, $\LMorse$ is
    \kl(language){bounded},\todo{This is false! there are chains that are unbounded languages?} 
    which is absurd by \cref{thue-morse:lemma}.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order
    type}, we conclude that the \kl{maximal order type} of $\LMorse$ is also $\omegaOrd$.
\end{proof}

>>>>

    Now, let us prove that these bounds are tight. It is clear that
    $\oHeight{\LMorse} = \omegaOrd$: given any number $n \in \Nat$, one can construct a
    \kl{decreasing sequence} of words in $\LMorse$ of length $n$, for instance by
    considering the first $n$ prefixes of the \kl{Thue-Morse sequence} by
    decreasing size.
    Let us now prove that $\oWidth{\LMorse} = \omegaOrd$. 
    To that end, we can leverage the fact that 
    the number of infixes of size $n$ in $\LMorse$ is bounded below by
    a non-constant affine function in $n$
    \cite{TRSHA95}, and that two words of length $n$ are comparable
    for the \kl{infix relation}
    if and only if they are equal. Hence, there cannot be a bound
    on the size of an \kl{antichain} in $\LMorse$, and we conclude
    that $\oWidth{\LMorse} = \omegaOrd$.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order
    type}, we conclude that the \kl{maximal order type} of $\LMorse$ is also $\omegaOrd$.
\end{proof}
